Understanding the impacts of video activity guides on parent-child interaction

### 2019-06-15 paper/cogsci2019/cogsci2019.tex
cleaning up intro

% Template for Cogsci submission with R Markdown

% Stuff changed from original Markdown PLOS Template
\documentclass[10pt, letterpaper]{article}

\usepackage{cogsci}
\usepackage{pslatex}
\usepackage{float}
\usepackage{caption}

% amsmath package, useful for mathematical formulas
\usepackage{amsmath}

% amssymb package, useful for mathematical symbols
\usepackage{amssymb}

% hyperref package, useful for hyperlinks
\usepackage{hyperref}

% graphicx package, useful for including eps and pdf graphics
% include graphics with the command \includegraphics
\usepackage{graphicx}

% Sweave(-like)
\usepackage{fancyvrb}
\DefineVerbatimEnvironment{Sinput}{Verbatim}{fontshape=sl}
\DefineVerbatimEnvironment{Soutput}{Verbatim}{}
\DefineVerbatimEnvironment{Scode}{Verbatim}{fontshape=sl}
\newenvironment{Schunk}{}{}
\DefineVerbatimEnvironment{Code}{Verbatim}{}
\DefineVerbatimEnvironment{CodeInput}{Verbatim}{fontshape=sl}
\DefineVerbatimEnvironment{CodeOutput}{Verbatim}{}
\newenvironment{CodeChunk}{}{}

% cite package, to clean up citations in the main text. Do not remove.
\usepackage{apacite}

% KM added 1/4/18 to allow control of blind submission
\cogscifinalcopy

\usepackage{color}

% Use doublespacing - comment out for single spacing
%\usepackage{setspace}
%\doublespacing

% % Text layout
% \topmargin 0.0cm
% \oddsidemargin 0.5cm
% \evensidemargin 0.5cm
% \textwidth 16cm
% \textheight 21cm

\title{Understanding the impact of electronically-delivered parenting advice}

\author{{\large\bf George~Kachergis} (\texttt{kachergis@stanford.edu}) \\ {\large\bf Hanwen Vivian~Zhang} (\texttt{vivian3@stanford.edu}) \\ {\large\bf Michael C.~Frank} (\texttt{mcfrank@stanford.edu}) \\  Department of Psychology, Stanford University \\  Stanford, CA 94305 USA}

\begin{document}

\maketitle

\begin{abstract}
Early parenting practices play an important role in shaping the future
outcomes of young children (Hart \& Risley, 1995; Heckman, 2006). In
particular, high-quality early interactions and language input appear to
facilitate language learning and result in higher levels of school
performance. The rise of phone- and tablet-based parenting applications
(``apps'') holds the promise of delivering low-cost, positive
interventions on parenting style to a wide variety of populations. Of
special interest are the parents of very young children, who are often
difficult to reach in other ways. Yet little is known about the effects
of communicating to parents through app-based interventions. In a study
of one commercial app offering a collection of age-appropriate activity
videos, we find that the quality of parent-child interactions increases
in some ways as a result of using the app. Specifically, the lexical
diversity of parents' child-directed speech increases, and measures of
joint attention show\ldots{}

\textbf{Keywords:}
digital parenting advice; joint attention; lexical diversity; guided
play;
\end{abstract}

\section{Introduction}\label{introduction}

Children of any given age show remarkable variability in their levels of
language proficiency (Fenson et al., 1994),

Young children spend a large portion of their waking time at play,
variously manipulating objects, exploring their environment, and
interacting with caregivers and peers. Playing with objects allows them
to discover hidden object properties and relations, and to build a
causal understanding of how objects interact (e.g., Schulz \& Bonawitz,
2007). Meanwhile, play also gives children an opportunity to set and
achieve goals (e.g., build a tower) and to practice a wide range of
motor skills (e.g., stacking) that will help them navigate the world
(Singer, Golinkoff, \& Hirsh-Pasek, 2006). Social play can help children
learn about human relationships, both through imitation of adult
behaviors and by experiencing and learning to process emotional events
such as failures (Singer et al., 2006). Of course, young children are
rarely playing in isolation: caregivers often provide encouragement and
guidance while scaffolding a child's play (Kaye, 1970; Wood, Bruner, \&
Ross, 1976). The quality of interactions during such guided play has
been shown to influence language learning: parents' joint attention to
objects that their child was focused on was positively correlated with
the child's subsequent vocabulary growth (M. Carpenter \& Tomasello,
1998; Tomasello \& Farrar, 1986). Episodes of joint attention during
guided play have also been found to contain more age-appropriate
advanced forms of play (Bigelow, MacLean, \& Proctor, 2004). More
generally, parenting practices early in childhood have been shown to
play an important role in shaping the future outcomes of young children
(Hart \& Risley, 1995; Heckman, 2006). While interventions often have
trouble reaching many parents of very young children, the proliferation
of mobile devices offers a good avenut for the digital delivery of
parenting advice (Breitenstein, Gross, \& Christophersen, 2014).
However, the efficacy of digital parenting advice has not been widely
proven.

\subsection{Guided Play Scaffolds
Learning}\label{guided-play-scaffolds-learning}

Children's early play behaviors are often assisted by more skilled and
knowledgeable play partners such as their caregivers and older siblings
(Kaye, 1970). Under such expert guidance, children are encouraged and
motivated to engage in more advanced play, undertaking explorations that
push the boundaries of what they would be able to do unaided (Vygotsky,
1980). These tutorial interactions have been shown to be important
components of child development (Wood et al., 1976). Thus, with the
knowledge of both play and tutorial interactions, guided play, which
consists of both active and enjoyable activities as well as close
guidance of adults (Hirsh-Pasek \& Golinkoff, 2008) has drawn
researchers' interest. A study of preschoolers showed that guided play
scaffolds the environment while still allowing children to maintain a
large degree of control, and it outperforms direct-instruction
approaches in encouraging a variety of positive academic outcomes
(Weisberg, Hirsh-Pasek, \& Golinkoff, 2013). Another study found that
guided play could facilitate children's vocabulary and comprehensive
language development and subsequent literacy skills (Massey, 2013).

\subsection{Improving Parenting Practices and Language
Use}\label{improving-parenting-practices-and-language-use}

Thus, including guided play in parenting practices from an early age may
boost children's language and educational outcomes. A recent home-visit
parenting practices intervention targeting children of low socioeconomic
status found that parents in the intervention group gained knowledge of
language development, and that this effect sustained four months after
the intervention (D. L. Suskind et al., 2015). However, although a
number of interactive measures increased during the experiment,
including the number of word tokens, conversational turns, and child
vocalizations, these increases did not sustain after the intervention.
That changes did not sustain could be due to the intervention itself, or
could merely be that the methods of home-visiting is not sustainable
enough for parents to easily and constantly get parenting advice. Thus,
new methods of delivering parenting advice should be considered.

\subsection{Effectiveness of Digital
Delivery}\label{effectiveness-of-digital-delivery}

With the widespread use of smartphones and tablets worldwide,
digitally-delivered interventions could address many of the logistical
barriers that have limited scaling up face-to-face delivery methods. A
review of 11 studies verified that digital delivery is a promising means
of effectively distributing interventions (Breitenstein et al., 2014).
However, the parent and child outcomes assessed in the review
(e.g.infant positive behaviors, satisfaction, emotional symptoms etc.)
did not address the nature or quality of parent-infant interactions at a
detailed level, like if the interventions lead to children paying more
attention, or vocabulary changes in parents' language usages. Although
digitally-delivered ac-tivities are designed to promote learning and
cognitive development, it is unclear how they might affect these
dimensions of parent-child interactions. Thus, we want to conduct this
experiment to explore if and how digital scaffolding of activities
affect the social and linguistic characteristics of parent-child
ineractions. The quality of parent-child interactions can be measured by
both the social engagement of parents (e.g., joint attention to objects
in the environment)(Bigelow et al., 2004) and the quality of language
(e.g., vocabulary diversity) (Malvern, Richards, Chipere, \& Durán,
2004).

\section{Experiment 1}\label{experiment-1}

@@

\subsection{Method}\label{method}

\subsubsection{Participants.}\label{participants.}

@@

\subsubsection{Materials.}\label{materials.}

@@

\subsection{Procedure.}\label{procedure.}

After providing informed consent, parents in the Video condition watched
the assigned activity video on a laptop with headphones. To ensure that
parents could give the video their full attention, the experimenter
played with the infant with a set of toys (different from the
experimental props used in the study) while the video was being played.
Immediately following the video, each parent-child dyad was provided
with the props to complete the activity they had viewed. The toys were
placed on a large foam mat, and parents were instructed to sit on the
mat with their child and re-create the activity they had viewed for a
period of three minutes. In the Control condition, after consenting
parents were told to play with their child as they would at home with
the provided props for a period of three minutes. They were not given
any additional instructions about how to use the props.

In both conditions, two video cameras were used to record the play
session from different angles, and parents were fitted with a wireless
audio recorder to record their child-directed speech. After three
minutes of play had elapsed, parents were told they could stop playing
and cameras and audio were turned off. Parents were then asked to
complete the PAQ before being debriefed.

\subsubsection{Joint Attention Coding
Procedure.}\label{joint-attention-coding-procedure.}

The video of each session was manually coded for episodes of joint
attention using the Datavyu software (Team, 2014). The video taken at
floor level was coded by default, but the other video was referred to if
the participants were not visible or if there was technical difficulty
with the first camera. Each session's video was coded for episodes of
coordinated joint attention, episodes of passive joint attention, and
parental bids for joint attention. Parental bids for joint attention
were defined as any attempt to initiate joint attention (i.e labeling,
pointing, or otherwise drawing attention to an object) that did not
result in passive or coordinated joint attention. If more than 3 seconds
elapsed between bids, they were coded as separate attempts. An episode
of joint attention was considered passive if both participants visually
focused on an object for a minimum of 3 seconds but the child did not
acknowledge the parent. If either participant looked away from the
object for less than 3 seconds and then returned to the same object it
was considered part of the same period of joint attention. A joint
attention episode was considered coordinated if both participants
visually focused on an object for a minimum of 3 seconds and at some
point in the interaction the child indicated awareness of interaction
with some overt behavior toward the parent such as looking at their
face, gesturing, vocalizing, or turn-taking.

@@

\section{Results}\label{results}

@@

\subsection{Lexical Diversity}\label{lexical-diversity}

@@

We fit a mixed-effects linear regression predicting TTR as a function of
condition, age (scaled and 0-centered), gender, and parent's education
level with a random intercept per video using lme4 (D. Bates, Mächler,
Bolker, \& Walker, 2015). There was significantly lower TTR in the Video
condition (mean: 0.32) than in the Control condition (mean: 0.43,
\(\beta=-.12\), t(39.9) = 4.25, \emph{p}\textless{}.001). There were no
significant effects of age, gender, or parent's level of education. A
similar mixed-effects linear regression instead predicting MTLD also
found significantly lower lexical diversity in the Video condition
(mean: 15.7) than in the Control condition (mean: 21.9,
\(\beta=-11.67\), t(43) = 3.08, \emph{p}\textless{}.01), with no other
significant effects. Figure 1 shows the mean of each lexical diversity
measure (TTR and MTLD) by condition.

@@

\begin{CodeChunk}
\begin{figure}[H]

@@

\caption[Mean lexical diversity scores by condition (left]{Mean lexical diversity scores by condition (left: Type/Token ratio, right: MTLD) in Experiment 1. Error bars show bootstrapped 95 percent confidence intervals (CIs).}\label{fig:e1lex_div}
\end{figure}
\end{CodeChunk}

@@

\caption[Mean number of word types and word tokens by condition in Experiment 1]{Mean number of word types and word tokens by condition in Experiment 1.}\label{fig:e1token_type}
\end{figure}
\end{CodeChunk}

\subsection{Joint Attention}\label{joint-attention}

We fit a mixed-effects linear regression predicting the number of bids
for joint attention (JA) as a function of fixed effects of condition,
age (scaled and 0-centered), gender, parent's education level, and the
subscales of the EPAQ: Early Learning (EL), Affection and Attachment
(AA), and Rules and Respect (RR), along with interactions of condition
and EL, AA, and RR. This lme4 model included random intercepts per
video. There were significantly more bids for JA in the Video condition
(mean: X) than in the Control condition (mean: X, \(\beta=3.51\),
t(40.3) = 2.95, \emph{p}\textless{}.01). There were no other significant
effects. Mixed-effects regressions with the same structure were
performed predicting the number of episodes of coordinated and passive
JA, and the total duration of time spent in coordinated and passive JA.
There were no significant effects on the number or total duration of
coordinated JA episodes, nor on the total duration of passive JA
episodes. For the regression predicting the number of passive joint
attention episodes, the only significant effect was an interaction of
condition and RR (\(\beta=1.83\), t(41.5) = 2.22,
\emph{p}\textless{}.05), showing that\ldots{} Figure X shows \ldots{} by
condition.

\begin{CodeChunk}
\begin{figure}[H]

@@

\caption[Mean number of bids and episodes of Joint Attention in Experiment 1]{Mean number of bids and episodes of Joint Attention in Experiment 1.}\label{fig:e1ja-graphs}
\end{figure}
\end{CodeChunk}

\begin{CodeChunk}
\begin{figure}[H]

@@

\caption[Average number of passive and coordinated episodes of JA in Experiment 1]{Average number of passive and coordinated episodes of JA in Experiment 1.}\label{fig:e1ja-graphs-pass-coord}
\end{figure}
\end{CodeChunk}

\subsection{Discussion}\label{discussion}

In summary, while the number of tokens and types were higher in the
experimental condition, lexical diversity (Type/Token ratio) was higher
in the control condition. Parents may be relatively more repetetive in
the experimental condition since they are attempting to stick to a
specific prescribed task, but they talk more overall. Demographics and
PAQ do not interact with condition, but there is a marginal effect of RR
score on lexical diversity (lower diversity for higher RR scores), and
marginal effects of parent education on word types and tokens (more
types and tokens for higher parent education).

@@

\section{Experiment 2}\label{experiment-2}

Experiment 1 found that compared to parents who played with children as
they normally would, parents who watched a Kinedu video spoke more words
overall, but had lower lexical diversity. Parents who watched a video
also made more bids for joint attention, although these bids did not
result in more episodes of joint attention compared to the control
group. Experiment 2 attempts to replicate the findings from Experiment 1
with a restricted number of preregistered predictions. We will
additionally include a second control condition, in which the same
activities are described in written form, rather than being demonstrated
in video. This manipulation will help determine what the contribution of
the video demonstration is in producing the observed effects on
parent-child interactions.

\subsection{Method}\label{method-1}

\subsubsection{Participants.}\label{participants.-1}

@@

\subsubsection{Materials.}\label{materials.-1}

The design of Experiment 2 was similar to that of Experiment 1, except
that instead of a No-Video control condition, parents instead watched a
video that was generally related to child development research, but did
not give any specific instructions about how to interact with infants or
children. This was to control for the possibility that differences in
language output and joint attention in Experiment 1 could be due to
simply cuing parents to think about infants' learning and cognitive
development. The videos presented in the Control Video condition were
media clips (available on YouTube) of developmental psychologists
explaining their research interleaved with footage of infants or
toddlers engaged in developmental research studies. Thus, the content of
the videos superficially matched those in the Activity Video condition,
but did not suggest any particular activities. The videos were trimmed
to approximately match the average video length in the Activity Video
condition around 1.5 minutes.

\subsubsection{Procedure.}\label{procedure.-1}

@@

\section{Results}\label{results-1}

@@

\subsection{Lexical Diversity}\label{lexical-diversity-1}

>>>>

\documentclass[]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\hypersetup{unicode=true,
            pdftitle={Understanding the impacts of video activity guides on parent-child interaction},
            pdfkeywords={digital parenting advice; joint attention; lexical diversity; guided
play;},
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

%%% Use protect on footnotes to avoid problems with footnotes in titles
\let\rmarkdownfootnote\footnote%
\def\footnote{\protect\rmarkdownfootnote}

%%% Change title format to be more compact
\usepackage{titling}

% Create subtitle command for use in maketitle
\providecommand{\subtitle}[1]{
  \posttitle{
    \begin{center}\large#1\end{center}
    }
}

\setlength{\droptitle}{-2em}

  \title{Understanding the impacts of video activity guides on parent-child
interaction}
    \pretitle{\vspace{\droptitle}\centering\huge}
  \posttitle{\par}
    \author{}
    \preauthor{}\postauthor{}
    \date{}
    \predate{}\postdate{}

\begin{document}
\maketitle
\begin{abstract}
Early parenting practices play an important role in shaping the future
outcomes of young children (Hart \& Risley, 1995; Heckman, 2006). In
particular, high-quality early interactions and language input appear to
facilitate language learning and result in higher levels of school
performance. The rise of phone- and tablet-based parenting applications
(``apps'') holds the promise of delivering low-cost, positive
interventions on parenting style to a wide variety of populations. Of
special interest are the parents of very young children, who are often
difficult to reach in other ways. Yet little is known about the effects
of communicating to parents through app-based interventions. In a study
of one commercial app offering a collection of age-appropriate activity
videos, we find that the quality of parent-child interactions increases
in some ways as a result of using the app. Specifically, the lexical
diversity of parents' child-directed speech increases, and measures of
joint attention show\ldots{}
\end{abstract}

\hypertarget{introduction}{%
\section{Introduction}\label{introduction}}

The quantity and quality of early language input has been found to be
strongly associated with later language and academic outcomes (Cartmill
et al., 2013; Hart \& Risley, 1995; Hirsh-Pasek et al., 2015; Marchman
\& Fernald, 2008). Thus, because of the potential for large downstream
effects (Heckman, 2006), there is tremendous interest in interventions
that change children's language environment. And because parents define
a large portion of that environment, especially before the onset of
formal schooling, parent behavior is a critical locus for such
interventions. Many effective parenting interventions require large
resource investments and require many hours of in-person contact
(Gertler et al., 2014; Schweinhart et al., 2004), making implementation
at scale a daunting proposition. For this reason, many researchers
targeting early language are interested in delivering parenting
interventions remotely -- through texts, apps, and videos delivered on
digital devices. But what do parents take away from these short messages
about what to do or how to talk with their children?

The content provided by digital parenting interventions runs the gamut
from general parenting messages and facts from child development
research to specific advice and suggested activities. A growing body of
evidence suggests that these digital interventions can be effective
across a range of cultures, income levels, and children's ages (for a
review, see )(Breitenstein, Gross, \& Christophersen, 2014). For
example, in contrast to a face-to-face parent training intervention, a
tablet-based version saw significantly higher session completion rates
(51\% attendance vs.~85\% module completion) and comparable or larger
effect sizes on parents' and children's (aged 2 to 5 years) behavior
(Breitenstein, Fogg, Ocampo, Acosta, \& Gross, 2016). Often, however,
the theory of change presupposed by such interventions is relatively
vague. Both within and outside the realm of academic interventions,
messages to parents of young children often seek to provide knowledge
about some aspect of development (e.g., early language), often in tandem
with a suggestion regarding activities. Such messages are assumed to
inform parents' choice of behaviors, spurring them to engage in the
target activity, which is assumed to be more stimulating than what
parents would have done otherwise.

This theory of change is grounded in ideas about guided play and early
language stimulation. Language input varies not only in quantity (i.e.,
the number of total tokens), but also in quality (i.e., the diversity of
the tokens) (Malvern, Richards, Chipere, \& Durán, 2004). Further,
language learning -- especially the acquisition of early vocabulary in
the first years -- appears to be supported preferentially by parents and
children \emph{jointly attending} to some object or activity (Bigelow,
MacLean, \& Proctor, 2004). Episodes of joint attention are frequent
during guided play, when parents set goals and scaffold their child's
activities (Weisberg, Hirsh-Pasek, \& Golinkoff, 2013; Wood, Bruner, \&
Ross, 1976). Thus, the current literature supports interventions that
encourage parents to provide high-quality language and interaction
through something like guided play -- whether via reading books or
playing with a shape-sorter at home, or via a conversation about
categories in the supermarket.

But is this theory of change correct? That is, does the provision of
knowledge and activities lead to higher-quality play? An alternative
hypothesis is that this theory could be wrong in a number of ways. By
focusing parents on a specific activity, they could over-focus on
achieving the superficial goals of the activity. This problem might be
especially likely with video messages, which could encourage parents to
try to mimic a model. And these misinterpretations in turn could result
in less high-quality talk, with less joint attention. Or, these messages
could produce the desired effect, but only for those parents who already
have a general orientation towards children's early learning.

Our current experiments were designed to make a direct test of this
question: How do parents change their interactions with young children
on the basis of short video parenting messages? In both studies, we
collected data from parent-child dyads in a local children's museum. We
showed parents in the experimental group a single short video modeling
an interactive toy-based activity along with a scientific justification.
Parents in the control group received either no video (Experiment 1) or
a video of a recent finding in developmental psychology (Experiment 2).
We then gave the toys from the video to all dyads and videotaped their
interactions, coding for language quantity and quality as well as joint
attention.

Under such expert guidance, children are encouraged and motivated to
engage in more advanced play, undertaking explorations that push the
boundaries of what they would be able to do unaided (Vygotsky, 1980).

But does providing such information change parents' behavior towards
young children? And is this advice effective in producing change along
the desired dimension? An alternative might be that asking parents to
focus on a specific activity that may be novel to them may tax their
cognitive resources, resulting in decreases in the quality of their
child-directed speech, or in less flexible, lower-quality social
interactions.

What are digital interventions With the widespread use of smartphones
and tablets worldwide, digitally-delivered interventions could address
many of the logistical barriers that have limited scaling up
face-to-face delivery methods. However, the parent and child outcomes
assessed in the review (e.g.infant positive behaviors, satisfaction,
emotional symptoms etc.) did not address the nature or quality of
parent-infant interactions at a detailed level, for example whether the
interventions lead to children paying more attention, or vocabulary
changes in parents' language usages. Although digitally-delivered
activities are designed to promote learning and cognitive development,
it is unclear how they might affect these dimensions of parent-child
interactions. Thus, we want to conduct this experiment to explore if and
how digital scaffolding of activities affect the social and linguistic
characteristics of parent-child ineractions. The quality of parent-child
interactions can be measured by both the social engagement of parents
(e.g., joint attention to objects in the environment)(Bigelow et al.,
2004) and the quality of language (e.g., vocabulary diversity) (Malvern
et al., 2004).

Communication and message content

In our study, we focus on videos that provide suggested play activities
to parents. These videos constitute a short-term ``guided play''
intervention.

Young children spend a large portion of their waking time at play,
variously manipulating objects, exploring their environment, and
interacting with caregivers and peers. Playing with objects allows them
to discover hidden object properties and relations, and to build a
causal understanding of how objects interact (e.g., Schulz \& Bonawitz,
2007). Meanwhile, play also gives children an opportunity to set and
achieve goals (e.g., build a tower) and to practice a wide range of
motor skills (e.g., stacking) that will help them navigate the world
(Singer, Golinkoff, \& Hirsh-Pasek, 2006). Social play can help children
learn about human relationships, both through imitation of adult
behaviors and by experiencing and learning to process emotional events
such as failures (Singer et al., 2006). Of course, young children are
rarely playing in isolation: caregivers often provide encouragement and
guidance while scaffolding a child's play (Kaye, 1970; Wood et al.,
1976). The quality of interactions during such guided play has been
shown to influence language learning: parents' joint attention to
objects that their child was focused on was positively correlated with
the child's subsequent vocabulary growth (M. Carpenter \& Tomasello,
1998; Tomasello \& Farrar, 1986). Episodes of joint attention during
guided play have also been found to contain more age-appropriate
advanced forms of play (Bigelow et al., 2004). More generally, parenting
practices early in childhood have been shown to play an important role
in shaping the future outcomes of young children (Hart \& Risley, 1995;
Heckman, 2006). While interventions often have trouble reaching many
parents of very young children, the proliferation of mobile devices
offers a good avenut for the digital delivery of parenting advice
(Breitenstein et al., 2014). However, the efficacy of digital parenting
advice has not been widely proven.

\hypertarget{guided-play-scaffolds-learning}{%
\subsection{Guided Play Scaffolds
Learning}\label{guided-play-scaffolds-learning}}

Children's early play behaviors are often assisted by more skilled and
knowledgeable play partners such as their caregivers and older siblings
(Kaye, 1970). Under such expert guidance, children are encouraged and
motivated to engage in more advanced play, undertaking explorations that
push the boundaries of what they would be able to do unaided (Vygotsky,
1980). These tutorial interactions have been shown to be important
components of child development (Wood et al., 1976). Thus, with the
knowledge of both play and tutorial interactions, guided play, which
consists of both active and enjoyable activities as well as close
guidance of adults (Hirsh-Pasek \& Golinkoff, 2008) has drawn
researchers' interest. A study of preschoolers showed that guided play
scaffolds the environment while still allowing children to maintain a
large degree of control, and it outperforms direct-instruction
approaches in encouraging a variety of positive academic outcomes
(Weisberg et al., 2013). Another study found that guided play could
facilitate children's vocabulary and comprehensive language development
and subsequent literacy skills (Massey, 2013).

\hypertarget{improving-parenting-practices-and-language-use}{%
\subsection{Improving Parenting Practices and Language
Use}\label{improving-parenting-practices-and-language-use}}

Thus, including guided play in parenting practices from an early age may
boost children's language and educational outcomes. A recent home-visit
parenting practices intervention targeting children of low socioeconomic
status found that parents in the intervention group gained knowledge of
language development, and that this effect sustained four months after
the intervention (Suskind et al., 2015). However, although a number of
interactive measures increased during the experiment, including the
number of word tokens, conversational turns, and child vocalizations,
these increases did not sustain after the intervention. That changes did
not sustain could be due to the intervention itself, or could merely be
that the methods of home-visiting is not sustainable enough for parents
to easily and constantly get parenting advice. Thus, new methods of
delivering parenting advice should be considered.

\hypertarget{effectiveness-of-digital-delivery}{%
\subsection{Effectiveness of Digital
Delivery}\label{effectiveness-of-digital-delivery}}

\hypertarget{experiment-1}{%
\section{Experiment 1}\label{experiment-1}}

@@

\hypertarget{method}{%
\subsection{Method}\label{method}}

\hypertarget{participants.}{%
\subsubsection{Participants.}\label{participants.}}

@@

\hypertarget{materials.}{%
\subsubsection{Materials.}\label{materials.}}

@@

\hypertarget{procedure.}{%
\subsubsection{Procedure.}\label{procedure.}}

After providing informed consent, parents in the Video condition watched
the assigned activity video on a laptop with headphones. To ensure that
parents could give the video their full attention, the experimenter
played with the infant with a set of toys (different from the
experimental props used in the study) while the video was being played.
Immediately following the video, each parent-child dyad was provided
with the props to complete the activity the parent had viewed. The toys
were placed on a large foam mat, and parents were instructed to sit on
the mat with their child and re-create the activity they had viewed for
a period of three minutes. In the Control condition, after consenting
parents were told to play with their child as they would at home with
the provided props for a period of three minutes. They were not given
any additional instructions about how to use the props.

In both conditions, two video cameras were used to record the play
session from different angles, and parents were fitted with a wireless
microphone (Shurre lavalier microphone) to record their child-directed
speech. After three minutes of play had elapsed, parents were told they
could stop playing and the cameras and microphone were turned off.
Parents were then asked to complete the EPAQ before being debriefed.

\hypertarget{joint-attention-coding-procedure.}{%
\subsubsection{Joint Attention Coding
Procedure.}\label{joint-attention-coding-procedure.}}

The video of each session was manually coded for episodes of joint
attention (JA) using the Datavyu software (Team, 2014). The video taken
at floor level was coded by default, but the other video was referred to
if the participants were not visible or if there was technical
difficulty with the first camera. Each session's video was coded for
episodes of coordinated JA, episodes of passive JA, and parental bids
for JA. Parental bids for JA were defined as any attempt to initiate
joint attention (i.e labeling, pointing, or otherwise drawing attention
to an object) that did not result in passive or coordinated JA. If more
than 3 seconds elapsed between bids, they were coded as separate
attempts. An episode of joint attention was considered passive if both
participants visually focused on an object for a minimum of 3 seconds
but the child did not acknowledge the parent. If either participant
looked away from the object for less than 3 seconds and then returned to
the same object it was considered part of the same period of joint
attention. A joint attention episode was considered coordinated if both
participants visually focused on an object for a minimum of 3 seconds
and at some point in the interaction the child indicated awareness of
interaction with some overt behavior toward the parent such as looking
at their face, gesturing, vocalizing, or turn-taking.

@@

\hypertarget{results}{%
\subsection{Results}\label{results}}

@@

\hypertarget{lexical-diversity}{%
\subsubsection{Lexical Diversity}\label{lexical-diversity}}

@@

We fit a mixed-effects linear regression predicting TTR as a function of
condition, age (scaled and 0-centered), gender, and parent's education
level with a random intercept per video using lme4 (Bates, Mächler,
Bolker, \& Walker, 2015). There was significantly lower TTR in the Video
condition (mean: 0.32) than in the Control condition (mean: 0.43,
\(\beta=-.12\), t(39.9) = 4.25, \emph{p}\textless{}.001). There were no
significant effects of age, gender, or parent's level of education. A
similar mixed-effects linear regression instead predicting MTLD also
found significantly lower lexical diversity in the Video condition
(mean: 15.7) than in the Control condition (mean: 21.9,
\(\beta=-11.67\), t(43) = 3.08, \emph{p}\textless{}.01), with no other
significant effects. Figure 1 shows the mean of each lexical diversity
measure (TTR and MTLD) by condition.

@@

\begin{figure}[H]

@@

\caption{Mean lexical diversity scores by condition (left: Type/Token ratio, right: MTLD) in Experiment 1. Error bars show bootstrapped 95 percent confidence intervals (CIs).}\label{fig:e1lex_div}
\end{figure}

@@

\caption{Mean number of word types and word tokens by condition in Experiment 1.}\label{fig:e1token_type}
\end{figure}

\hypertarget{joint-attention}{%
\subsubsection{Joint Attention}\label{joint-attention}}

We fit a mixed-effects linear regression predicting the number of bids
for joint attention (JA) as a function of fixed effects of condition,
age (scaled and 0-centered), gender, parent's education level, and the
subscales of the EPAQ: Early Learning (EL), Affection and Attachment
(AA), and Rules and Respect (RR), along with interactions of condition
and EL, AA, and RR. This lme4 model included random intercepts per
video. There were significantly more bids for JA in the Video condition
(mean: 6.24, sd: 2.79) than in the Control condition (mean: 3.56, sd:
2.50, \(\beta=3.51\), t(40.3) = 2.95, \emph{p}\textless{}.01). There
were no other significant effects. Mixed-effects regressions with the
same structure were performed predicting the number of episodes of
coordinated and passive JA, and the total duration of time spent in
coordinated and passive JA. There were no significant effects on the
number or total duration of coordinated JA episodes, nor on the total
duration of passive JA episodes. For the regression predicting the
number of passive JA episodes, the only significant effect was an
interaction of condition and RR (\(\beta=1.83\), t(41.5) = 2.22,
\emph{p}\textless{}.05), showing that for parents in the Video
condition, those with higher Rules and Respect subscores engaged in more
passive JA episodes. Figure X shows \ldots{} by condition.

\begin{figure}[H]

@@

\caption{Mean number of bids and episodes of Joint Attention in Experiment 1.}\label{fig:e1ja-graphs}
\end{figure}

\begin{figure}[H]

@@

\caption{Average number of passive and coordinated episodes of JA in Experiment 1.}\label{fig:e1ja-graphs-pass-coord}
\end{figure}

\hypertarget{discussion}{%
\subsection{Discussion}\label{discussion}}

In summary, while parents produced more word types and tokens after
viewing the activity video, lexical diversity (Type/Token ratio and
MTLD) was higher when parents were just asked to play as they normally
would. This may suggest that parents in the Video condition are being
more repetitive in their attempt to stick to the task prescribed in the
video. Demographics and EPAQ do not interact with condition, but there
is a marginal effect of RR score on lexical diversity (lower diversity
for higher RR scores), and marginal effects of parent education on word
types and tokens (more types and tokens for higher parent education).

@@

\hypertarget{experiment-2}{%
\section{Experiment 2}\label{experiment-2}}

Experiment 1 found that parents who watched a Kinedu video spoke more
words overall, but had lower lexical diversity compared to parents who
played with their children as they normally would at home. Parents who
watched a Kinedu video also made more bids for joint attention, although
these bids did not result in more episodes of joint attention compared
to the control group. Experiment 2 attempts to replicate these findings
from with a restricted number of preregistered predictions
(\href{https://osf.io/2bpdf/}{link}).

\hypertarget{method-1}{%
\subsection{Method}\label{method-1}}

\hypertarget{participants.-1}{%
\subsubsection{Participants.}\label{participants.-1}}

@@

\hypertarget{materials.-1}{%
\subsubsection{Materials.}\label{materials.-1}}

The design of Experiment 2 was similar to that of Experiment 1, except
that instead of a No-Video control condition, parents instead watched a
video that was generally related to child development research, but did
not give any specific instructions about how to interact with infants or
children. This was to control for the possibility that differences in
language output and joint attention in Experiment 1 could be due to
simply cuing parents to think about infants' learning and cognitive
development. The videos presented in the Control Video condition were
media clips (available on YouTube) of developmental psychologists
explaining their research interleaved with footage of infants or
toddlers engaged in developmental research studies. Thus, the content of
the videos superficially matched those in the Activity Video condition,
but did not suggest any particular activities. The videos were trimmed
to approximately match the average video length in the Activity Video
condition (close to 90 s).

\hypertarget{procedure.-1}{%
\subsubsection{Procedure.}\label{procedure.-1}}

@@

\hypertarget{results-1}{%
\subsection{Results}\label{results-1}}

@@

\hypertarget{lexical-diversity-1}{%
\subsubsection{Lexical Diversity}\label{lexical-diversity-1}}
